Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-09-10 paper/post_tci.tex
typo in caption of Fig 2 fixed.

 \begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
        \caption{Illustration of the use of priors in reconstruction
          as the number of views reduces. For all cases, the ground
          truth (260$\times$260) appears in the top left.  For
          extremely large number of views (800 views), the standard
          FBP reconstruction (first column) is of very good quality
          (Structural Similarity Index Metric, SSIM=0.92). As the
          number of views become limited (100 views), reconstruction
          using the Total Variation regularization prior (TV, middle
          column) is better both visually and quantitatively than FBP
          (SSIM of 0.96 vs 0.82). If the number of views is
          drastically reduced (20 views), the presence of both TV
          prior and object- prior together with the spatially-varying
          technique of this paper improves the reconstruction
          (SSIM=0.91) when compared to presence of TV-only prior
          (SSIM=0.87) or no prior (SSIM=0.64).}
 \label{fig:story}
 \end{figure}

@@

 \begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
        \caption{Overview of our work. (Upper) When the number of
          measurements is vastly lower than what is conventionally
          used (last column of Fig.~\ref{story}) a regularization
          prior such as Total Variation alone is not sufficient to
          mitigate the sub-sampling artefacts. (Lower) An object-prior
          must be used to provide additional information, but in
          addition, new bias should not be introduced. To this end,
          here we propose using a spatially-varying weights-map to
          modulate the effect of object-prior on the final
          reconstruction.}
 \label{fig:prior_overview}
\end{figure}

>>>>

 \begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
        \caption{Illustration of the use of priors in reconstruction
          as the number of views reduces. For all cases, the ground
          truth (260$\times$260) appears in the top left.  For
          extremely large number of views (800 views), the standard
          FBP reconstruction (first column) is of very good quality
          (Structural Similarity Index Metric, SSIM=0.92). As the
          number of views become limited (100 views), reconstruction
          using the Total Variation regularization prior (TV, middle
          column) is better both visually and quantitatively than FBP
          (SSIM of 0.96 vs 0.82). If the number of views is
          drastically reduced (20 views), the presence of both TV
          prior and object-prior together with the spatially-varying
          technique of this paper improves the reconstruction
          (SSIM=0.91) when compared to presence of TV-only prior
          (SSIM=0.87) or no prior (SSIM=0.64).}
 \label{fig:story}
 \end{figure}

@@

 \begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
        \caption{Overview of our work. (Upper) When the number of
          measurements is vastly lower than what is conventionally
          used (last column of Fig.~\ref{fig:story}) a regularization
          prior such as Total Variation alone is not sufficient to
          mitigate the sub-sampling artefacts. (Lower) An object-prior
          must be used to provide additional information, but in
          addition, new bias should not be introduced. To this end,
          here we propose using a spatially-varying weights-map to
          modulate the effect of object-prior on the final
          reconstruction.}
 \label{fig:prior_overview}
\end{figure}
